Low Complexity Adaptive Sonar Imaging

### 2016-03-02 LCAforActiveSonarImaging/submission/submit1/answer/answer.tex
la2pdf commit - 2016:03:02	08:53:57	(on. 2.mars)

\begin{enumerate}
% \emph{General}
\hi{Introduction}
\qi{The authors show no evidence that bats use adaptive processing, remove this example.}
\ai{The reviewer makes a good point, this may not have been obvious. We have provided a reference for the adaptive processing used by bats, but would prefer to keep the example if possible.}
%
\qi{It is not clear whether LCA is really an adaptive method that adapts weights on the fly or a method that a posteriori decides which window shows best results.}
\ai{We appreciate the remark. We are using a system level definition of adaptivity that includes any kind of dynamic and data dependent behaviour, hence feel that both beamformers fall in that category. Both methods process the pixels in a data dependent manner, and result in non linear image. However, perhaps it should be made even clearer that the LCA solution space is a sampled version of that of MVDR. We will attempt to express this better.}
%
\qi{The use of non-SI units like cm is discouraged.}
\ai{We agree that non-SI units should be avoided, however had the belief that cm being a prefixed SI unit was valid? In the IEEE Styles Manual this unit is used several times as an example: 
\url{http://www.ieee.org/publications_standards/publications/journmag/online_style_manual-10292015.pdf} (e.g. on page 24 paragraph ``The En, Em, or Two-Em Dash'', and several times on page 25 paragraph ``Math'' bullet point 16). Will leave this as is for now pending any objections?}
%
\end{enumerate}

@@

\ans{We thank the reviewer for the thorough review and very constructive remarks. We believe in this philosophy and will make changes accordingly.}

>>>>

\begin{enumerate}
% \emph{General}
\hi{Introduction}
\qi{The authors show no evidence that bats use adaptive processing, remove this example.}
\ai{The reviewer makes a good point, this may not have been obvious. We have provided a reference for the adaptive processing used by bats, but would prefer to keep the example if possible.}
%
\qi{It is not clear whether LCA is really an adaptive method that adapts weights on the fly or a method that a posteriori decides which window shows best results.}
\ai{We appreciate the remark. We are using a system level definition of adaptivity that includes any kind of dynamic and data dependent behaviour, hence feel that both beamformers fall in that category. Both methods process the pixels in a data dependent manner, resulting in non linear image. We have tried to express it clearer that the LCA solution space is merely a sampled version of that of MVDR, hence can not be considered fully adaptive such as MVDR (although this, too, is heavily constrained).}
%
\qi{The use of non-SI units like cm is discouraged.}
\ai{We agree that non-SI units should be avoided, however had the belief that cm being a prefixed SI unit was valid? In the IEEE Styles Manual this unit is used several times as an example: 
\url{http://www.ieee.org/publications_standards/publications/journmag/online_style_manual-10292015.pdf} (e.g. on page 24 paragraph ``The En, Em, or Two-Em Dash'', and several times on page 25 paragraph ``Math'' bullet point 16). Will leave this as is for now pending any objections?}
%
\end{enumerate}

@@

\ans{We thank the reviewer for the thorough review and very constructive remarks. We believe in this philosophy and attempt to make changes accordingly.}
